---
title: "Office Project"
author: "Josh Kong"
date: "6/15/2020"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r}
library(tidytext)
library(schrute)
library(tidyverse)
office_transcripts <- as_tibble(theoffice) %>%
  mutate(season = as.integer(season),
         episode = as.integer(episode)) %>%
  mutate(character = str_remove_all(character, '"')) %>%
  mutate(name = str_to_lower(str_remove_all(episode_name, "\\.| \\(Part.*")))

office_ratings <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-03-17/office_ratings.csv') %>%
  mutate(name = str_to_lower(str_remove_all(title, "\\.| \\(Part.*|\\: Part.*")))

```

## Ratings of the Office by Episode and Season 

```{r}
# Looking at the office ratings per season
office_ratings %>% 
  group_by(season) %>% 
  summarise(avg_ratings = mean(imdb_rating)) %>% 
  ggplot(aes(season,avg_ratings)) + geom_line() +
  scale_x_continuous(breaks=1:9)
```

```{r}
# Looking at the office ratings per episode using a bar graph

office_ratings %>% 
  mutate(title = fct_inorder(title)) %>% 
  ggplot(aes(title,imdb_rating, fill = factor(season)))+
  geom_col()+
  theme(axis.text.x = element_blank())
```

```{r,fig.width=15}
#this plot shows the trend that the office ratings follow along with the episode names
office_ratings %>% 
  mutate(title = fct_inorder(title), episode_num = row_number()) %>% 
  ggplot(aes(episode_num,imdb_rating)) +
  geom_line(group = 1) +
  geom_smooth() +
  geom_point(aes(color = factor(season),size = total_votes)) +
  geom_text(aes(label = title),check_overlap = TRUE)+
  theme(panel.grid.major.x = element_blank(),
        panel.grid.major.y = element_blank())+
  labs(x = "Episode Number", y = "IMDB Ratings")
```


```{r}
#looking at the top 20 rated office episodes
office_ratings %>% 
  arrange(desc(imdb_rating)) %>% 
  mutate(title = paste0(season,".",episode," ",title), title = fct_inorder(title)) %>% 
  head(20) %>% 
  ggplot(aes(title,imdb_rating)) + geom_point(aes(color = factor(season))) + coord_flip()

          #NOTE, no episodes from season 1 or 8 are in the top 20 episodes 
```



## Looking at the office transcripts


```{r}
#use %in% if you want to do == for a vector!!!
blacklist <- c("yeah", "hey", "uh", "gonna")
blacklist_characters <- c("Everyone", "All", "Both", "Guy", "Girl", "Group")

transcript_words <- office_transcripts %>% 
  group_by(character) %>% 
  filter(n()>=100,
         n_distinct(episode_name) > 2) %>% 
  ungroup() %>% 
  select(-text_w_direction) %>% 
  unnest_tokens(word,text) %>% 
  anti_join(stop_words, by = "word") %>% 
  filter(!word %in% blacklist,
         !character %in% blacklist_characters)

  
character_words <- transcript_words %>% 
  count(character, word, sort = TRUE)

#looking at some of the most common words said by major characters
character_words %>% 
  filter(character %in% c("Michael", "Jim", "Pam", "Dwight")) %>% 
  group_by(character) %>% 
  top_n(10) %>% 
  ungroup() %>% 
  ggplot(aes(word,n)) +geom_col()+ coord_flip() + facet_wrap(~character,scales = "free")

 
```

NOTE: 

I decided to blacklist some characters such as "Everyone" and "All" because they are not an actual character in the show. 

I also decided to blacklist some words such as "hey" and "yea" because they are words that appeared a lot, but do not seem to be words that are really significant.


## What are some of the things that affect the ratings of an episode?

Some of the things that we can observe are 

- Season 
- Director
- Writers
- Lines per character in the episode

```{r}
#begin by joining the datasets of office transcripts and office ratings

#trying to see if there is a relationship between popular characters and ratings
#character must have at least 50 lines and must appear in at least 5 episodes to qualify
ratings_summarized <- office_ratings %>%
  group_by(name) %>%
  summarize(imdb_rating = mean(imdb_rating))

character_lines_ratings <- office_transcripts %>%
  filter(!character %in% blacklist_characters) %>%
  count(character, name) %>%
  group_by(character) %>%
  filter(sum(n) >= 50,
         n() >= 5) %>% 
  inner_join(ratings_summarized, by = "name")


character_lines_ratings %>%
  summarize(avg_rating = mean(imdb_rating),
            nb_episodes = n()) %>%
  arrange(desc(avg_rating))

```

Now looking at directors and writers

```{r}
director_writer_features <- office_transcripts %>%
  distinct(name, director, writer) %>%
  gather("type", "value", director, writer) %>%
  separate_rows(value, sep = ";") %>%
  unite(feature, type, value, sep = ": ") %>%
  group_by(feature) %>%
  filter(n() >= 3) %>%
  mutate(value = 1) %>%
  ungroup()

character_line_features <- character_lines_ratings %>%
  ungroup() %>%
  transmute(name, feature = character, value = n)

season_features = office_ratings %>%
  distinct(name, season) %>%
  transmute(name, feature = paste("season:", season), value = 1)
features <- bind_rows(director_writer_features,
                      character_line_features,
                      season_features) %>%
  semi_join(office_ratings, by = "name") %>%
  semi_join(office_transcripts, by = "name")
view(features)
episode_feature_matrix <- features %>%
  cast_sparse(name, feature, value)

ratings <- ratings_summarized$imdb_rating[match(rownames(episode_feature_matrix), ratings_summarized$name)]

```


## Machine Learning: Ridge Regression

Want to see the effect of a character, season, writer, and director on the rating of an office episode


```{r}
library(glmnet)
library(broom)
mod <- cv.glmnet(episode_feature_matrix, ratings)
plot(mod)
tidy(mod$glmnet.fit) %>%
  filter(lambda == mod$lambda.min,
         term != "(Intercept)") %>%
  mutate(term = fct_reorder(term, estimate)) %>%
  ggplot(aes(term, estimate, fill = estimate > 0)) +
  geom_col() +
  coord_flip() +
  labs(y = "Estimated effect on the rating of an episode") +
  theme(legend.position = "none")

```

Looking at the graph, it appears that when Steve Carell is a director, or Greg Daniels is the writer,
the episode tends to do very well. 

It appears that when Allison Silverman is a writer, or the episode is in season 1, the episode tends to do
poorly.


















